\section*{Team}

Our work will be a major step towards visualization systems that support analysis at the rate of thought.  For this kind of work to succeed, it is critical to have an interdisciplinary team with expertise in both Human-Computer Interaction and Data Management Systems. Our experience across these areas makes our team a strong candidate to tackle these challenges.  In addition, at the University of Washington we have strong collaborators in the Interactive Data Lab, the Database Group, and the eScience Institute.

\textbf{Kanit Wongsuphasawat} is a Ph.D. student in Computer Science \& Engineering and a member of the Interactive Data Lab at the University of Washington.  Kanit has expertise in Human-Computer Interaction and Visualization.  He is a co-developer of a declarative model for interactive visualization design \cite{satyanarayan:reactive-vega}.  Kanit has been awarded a Fulbright Fellowship and H.M. the King of Thailand scholarship.  He also has professional experience working in leading data-driven companies including Google, Tableau Software and Trifacta.

\textbf{Dominik Moritz} is a Ph.D. student in Computer Science \& Engineering at the University of Washington.   As a member of both the Database group and the Interactive Data Lab, Dominik has a strong background in data management systems and visualization.  He co-develops Myria, a distributed database system \cite{halperin:myria} and was a core developer of CKAN and creator of a number of libraries for data management and sharing. He has been awarded a Fulbright Fellowship and a scholarship from the German National Academic Foundation.